\begin{flushleft}
	\begin{thebibliography}{99}
			
		\bibitem{cormick-1987}
			McCORNICK, B. H. {\it Visualization in Scientific Computing.}\\
			 Computer Graphics, 21, 6 (listopad 1987).\\
			ACM SIGGRAPH, New York City, New York, 1987.
			
		\bibitem{aigner-2011}
			AIGNER, W. -- MIKSCH, S. -- SCHUMANN, H. -- TOMINSKI, Ch. {\it Visualization of Time-Oriented Data}.\\
			Springer Science \& Business Media, New York City, New York, 2011.\\
			ISBN10: 0857290797, ISBN13: 9780857290793.
			
		\bibitem{grafton-2013}
			GRAFTON, A. -- ROSENBERG D.\\
			{\it Cartographies of Time: A History of the Timeline}.\\
			Princeton Architectural Press, Princeton, New Jersey, 2013.\\
			ISBN10: 1568987633, ISBN13: 9781568987637.
			
		\bibitem{ferguson-1991}
			FERGUSON, S. {\it The 1753 Carte chronographique of Jacques Barbeu-Dubourg}.\\
			Friends of the Princeton University Library, Princeton, New Jersey, 1991.\\
		
		\bibitem{trettien-2009}
			TRETTIEN, W. {\it Timeline Visualizations: A Brief and Incomplete Teleological History} [část I] [online].\\
			Hyperstudio, MIT, Boston, Massachusetts, 4.\ts11.\ts2009 [cit.18.\ts4.\ts2015].\\
			Dostupné z: \url{http://hyperstudio.mit.edu/blog/blog-research/timeline-visualizations-a-brief-and-incomplete-}\\
			\url{teleological-history-part-1}
		
		\bibitem{temple}
			INGARGIOLA, G. {\it CIS 307: Precedence Graphs, Concurrency Grain, Fork and Join, CoBegin CoEnd} [online].\\
			CIS, Temple University, Philadelphia, Pensylvánie [cit.\ts19. 4. 2015].\\
			Dostupné z: \url{http://www.cis.temple.edu/~giorgio/old/cis307s96/readings/precedence.html}
			
		\bibitem{w3c-2014}
			{\it HTML5} [online].\\
			© W3C, 2014 [cit. 6.\ts3.\ts2015]\\
			Dostupné z \url{http://w3.org/TR/html5}
			
		\pagebreak
		
		
		\bibitem{opera-2010}
			SUCAN, M. {\it Choosing Between the Two} [online].\\
			©2006--2015, Opera Software ATA, 16.\ts6.\ts2010 [cit. 20.\ts4.\ts2015].\\
			Dostupné z: \url{https://dev.opera.com/articles/svg-or-canvas-choose}
		\bibitem{iso-8601}
			{\it ISO 8601:2004 -- Date and time format}.\\
			© ISO, 19.\ts6.\ts2013 [cit. 20.\ts4.\ts2015].

		\bibitem{poupa-2008}
			POUPA, M. {\it Časoměrný systém SEČ a přestupná sekunda} [online].\\
			ZČU, Plzeň, 2008 [cit. 27.\ts4.\ts2015].\\
			Dostupné z: \url{http://home.zcu.cz/~poupa/sec.html}
			
		\bibitem{simpson-2012}
			SIMPSON, K. {\it JavaScript and HTML5 Now}.\\
			O'Reilly Media, Inc., Newton, Massachusetts, 2012. 1. vydání.\\
			ISBN10: 1449339069.
			
		\bibitem{smart-insights-2015}
			BOSOMWORTH, D. {\it Mobile marketing statistics 2015} [online].\\
			© SmartInsights, Ltd, 15.\ts1.\ts2015 [cit. 28.\ts3.\ts2015].\\
			Dostupné z: \url{http://smartinsights.com/mobile-marketing/mobile-marketing-analytics/mobile-marketing-statistics}
			
		\bibitem{kogent-2008}
			Kogent Solutions Inc. {\it Ajax Black Book, New Edition}.\\
			Dreamtech Press, Nové Dillí, Indie, 2008.\\
			ISBN10: 8177228382, ISBN13: 9788177228380.
			
		\bibitem{w3c-jquery}
			{\it jQuery Introduction}. W3Schools [online].\\
			© Refsnes Data, 2015 [cit. 30.\ts5.\ts2015].\\
			Dostupné z: \url{http://www.w3schools.com/jquery/jquery_intro.asp}
		
		\bibitem{jqueryui-2015}
			{\it Getting Started with jQuery UI} [online].\\
			© The jQuery Foundation, 2015 [cit. 30.\ts5.\ts2015].\\
			Dostupné z: \url{http://learn.jquery.com/jquery-ui/getting-started}
			
		\bibitem{w3schools-js}
			{\it JavaScript Where To}. W3Schools [online].\\
			© Refsnes Data, 2015 [cit. 30.\ts5.\ts2015].\\
			Dostupné z: \url{http://www.w3schools.com/js/js_whereto.asp}
			
		\bibitem{requirejs}
			BURKE, J. {\it RequireJS} [online] [cit. 30.\ts5.\ts2015].\\
			Dostupné z: \url{http://requirejs.org}
			
		\bibitem{ecma-2011}
			{\it ECMAScript® Language Specification} [online].\\
			© Ecma International, Ženeva, Švýcarsko, 2011 [cit. 30.\ts5.\ts2015].\\
			Kapitola 15.9. Dostupné z: \url{http://www.ecma-international.org/ecma-262/5.1/Ecma-262.pdf}
			
		\pagebreak
		
		\bibitem{techrep-2013}
			PATTON, T. {\it Moment.js simplifies working with date values in JavaScript}. Software Engineer [online].\\
			© CBS Interactive, San Francisco, Kalifornie, 8.\ts7.\ts2013 [cit. 30.\ts5.\ts2015].\\
			Dostupné z: \url{http://www.techrepublic.com/blog/software-engineer/momentjs-simplifies-working-with-date-values-in-javascript}
			
		\bibitem{mozdev-js-intro}
			{\it A re-introduction to JavaScript} [online].\\
			© Mozilla Developer	Newtwork and individual distributors, posl. úprava 26.\ts4.\ts2015 [cit. 31.\ts5.\ts2015].\\
			Dostupné z: \url{https://developer.mozilla.org/cs/docs/Web/JavaScript/A_re-introduction_to_JavaScript}
			
		\bibitem{w3c-browser}
			{\it Browser Statistics} [online].\\
			© Refsnefs Data, 2015 [cit. 31.\ts5.\ts2015].\\
			Dostupné z: \url{http://www.w3schools.com/browsers/browsers_stats.asp}
			
		\bibitem{aristotheles}
			VOJÁČEK, J. {\it Aritmetická posloupnost a aritmetická řada} [online].\\
			© maths.cz, 2010 [cit. 24.\ts6.\ts2015].\\
			Dostupné z: \url{http://maths.cz/clanky/aritmeticka-posloupnost-a-aritmeticka-rada.html}
			
		\bibitem{soshnikov}
			SOSHNIKOV, D. {\it Closures}. ECMA-262-3 in detail [online].\\
			© Dmitry A. Soshnikov, 2012 [cit. 7.\ts6.\ts2015].\\
			Dostupné z: \url{http://dmitrysoshnikov.com/ecmascript/chapter-6-closures}
			
		\bibitem{moment-doc}
			{\it Docs}. Moment.js [online].\\
			© Tim Wood, Iskren Chernev, Moment.js contributors, 2015 [cit. 21.\ts6.\ts2015].\\
			Dostupné z: \url{http://momentjs.com/docs}
			
		\bibitem{snapsvg-why}
			{\it Why Snap.} Snap.svg [online].\\
			Dmitry Baranovskiy, 2015 [cit. 22.\ts6.\ts2015].\\
			Dostupné z: \url{http://snapsvg.io/about}
			
		\bibitem{jsdoc}
			{\it Using namepaths with JSDoc 3}. Use JSDoc [online].\\
			© The contributors to the JSDoc 3 doc. project [cit. 23.\ts6.\ts2015].\\
			Dostupné z: \url{http://usejsdoc.org/about-namepaths.html}
		
		%\bibitem{nazev_ukazatele}
		%	NOVÁK, J. -- NOVÁKOVÁ, M. {\it Název práce} [online].\\
		%	Země: Nakladatel, 2015. ©2015 Majitel copyrightu, 6. vydání / poslední změna 6.3.2015 [cit. 6.3.2015].\\
		%	ISBN: 1111111111.
		%	Dostupné z: webové stránky
			
	\end{thebibliography}
\end{flushleft}